%------------------------
% Resume in Latex
% Author : Harshibar
% Based off of: https://github.com/jakeryang/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}


% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top row of resume entry
      \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%       #1 & {\color{dark-grey}} \\
%     \end{tabular*}\vspace{-4pt}
% }
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\  % Include #2 for the date range
    \end{tabular*}\vspace{-4pt}
}


% \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
% \newcommand{\resumeSubItem}[1]{\hspace{2em} \resumeItem{#1}\vspace{-4pt}}
% \newcommand{\resumeSubItem}[1]{
%   \item[] \hspace{2em} \small{#1 \vspace{-1pt}}
% }
\newcommand{\resumeSubItem}[1]{
  \begin{itemize}
    \item \small{#1 \vspace{-1pt}}
  \end{itemize}
}


\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setlength{\footskip}{5pt}
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Joe (Yung-Hung) Huang} \\ \vspace{5pt}    
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{\href{mailto:yunghunghuang984@gmail.com}{yunghunghuang984@gmail.com}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \texttt{\href{https://github.com/hong539}{hong539}} \hspace{1pt} $|$
    %\hspace{1pt} \faYoutube \hspace{2pt} \texttt{harshibar} \hspace{1pt} $|$
    \hspace{1pt} \faMapMarker* \hspace{2pt}\texttt{Taiwan (R.O.C) Taipei}
    \\ \vspace{-3pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
  \resumeSubHeadingListStart

  \resumeSubheading
  {System/DevOps Engineer}{Jun. 2025 -- Current}
  {Logic Solutions Inc.}{}  
  \resumeItemListStart
    \resumeItem{\textbf{Quantum Product Systems} on \textbf{AWS, On-premise}}
      \resumeSubItem{Building system on AWS with \textbf{Gitlab/Terraform/Terragrunt/AtlantisTerraform Pull Request Automation/Packer}}
      \resumeSubItem{Development and Operation Automation tasks with \textbf{Ansible}}      
      \resumeSubItem{Building CI/CD pipelines with \textbf{Jenkins/Groovy scripts}}
      \resumeSubItem{Extend Observability with \textbf{Grafana/Prometheus/*-exporters/Alertmanager/Consul}}      
      \resumeSubItem{\textbf{Tech Stack}: Linux, Windows Server, AWS, Gitlab, Terraform, Terragrunt, AtlantisTerraform Pull Request Automation, Packer, Ansible, Jenkins, Groovy, Bash, Python, Golang, JavaScript/TypeScript, Angular, Java, Spring Boot, Flyway, MySQL, Microsoft SQL Server, RabbitMQ, Bash, Docker, Kubernetes...etc}
  \resumeItemListEnd

  \resumeSubheading
  {System/Site Reliability Engineering (SRE)/DevOps Engineering}{Nov. 2023 -- Dec. 2024}
  {Mending Technology CO., LTD.}{}  
  \resumeItemListStart
    \resumeItem{\textbf{Cryptocurrency Exchange System} on \textbf{AWS, On-premise} with more than \textbf{200 EC2/EKS/VM nodes} across \textbf{development, test, staging and production environments.}}
      \resumeSubItem{Participated in \textbf{Deployment of On-premise self-managed: Kubernetes cluster via Kubeadm/MetalLB/VMware vSphere, MySQL, RocketMQ, Redis, Nacos, Harbor}...etc.}
      \resumeSubItem{Participated in \textbf{the cross-AWS account service migration in a production environment.} Used \textbf{Pulumi alongside Ansible} to provision \textbf{AWS EC2 resources.}}
      \resumeSubItem{\textbf{Implemented an automated provisioning workflow} for various \textbf{AWS resources (AWS IAM, EC2, Aurora MySQL, Route53...etc)} in a \textbf{staging environment} using \textbf{Pulumi with Python scripts, Ansible playbooks.}}
      \resumeSubItem{Contributed to \textbf{optimizing and improving the CI pipeline} for the Java development team, providing demonstration workflows and best practices via \textbf{Gitlab CI and many other related Tools.}}
      \resumeSubItem{\textbf{Tech Stack}: Vue, PHP, Golang, Gin, Java, Spring Boot, Nacos, RocketMQ, Redis, Aurora MySQL, Python, Bash, Yaml, JSON, Linux, AWS, Gitlab, Docker, Kubernetes...etc}
  \resumeItemListEnd

  \resumeSubheading
  {Site Reliability Engineering (SRE)/DevOps/Cloud engineering}{Nov. 2021 -- April. 2023}
  {CloudRock Technology Co., Ltd}{}  
  \resumeItemListStart
    \resumeItem{Based on project characteristics and client requirements (e.g., \textbf{chatting and social apps, payment systems, sports data platforms, live streaming services, etc.}), assisted in system migration, deployment, and refactoring across multiple cloud environments, including \textbf{AWS, GCP, Alibaba Cloud, CloudFlare, and other public cloud services}.}      
      \resumeSubItem{Implemented CNCF-compliant system architectures by progressively introducing \textbf{Docker containerization, Kubernetes, and the Ingress-Nginx/Cert-Manager stack} in different phases of the system development lifecycle.}
      \resumeSubItem{Built systems using common cloud services such as \textbf{EC2, EKS, GKE, ACL, ELB, RDS...etc}, along with self-hosted services like \textbf{Nacos, RocketMQ, Redis, etc.}}
      \resumeSubItem{Maintained Kubernetes clusters for multiple client projects and provided optimization and troubleshooting solutions.}
      \resumeSubItem{Assisted in building and maintaining Gitlab or Jenkins CI/CD pipelines for client projects, including optimizing \textbf{.gitlab-ci.yml} Bash scripts for GitLab Runner, significantly reducing \textbf{cross-region network latency} issues.}
      \resumeSubItem{\textbf{Tech Stack}: Java, Spring Boot, Spring Cloud, Golang, PHP, JavaScript, Yaml, Prometheus, Grafana, ELK stack, AWS, GCP, Alibaba Cloud, CDNetworks, Linux, Docker, Kubernetes(GKE, EKS, ACK)...etc}
    \resumeItem{Development in a \textbf{Python Automation Project:} \textbf{boce-crawler}}
      \resumeSubItem{Building a crontab task based on a \textbf{Python} program to extract network metrics from 3rd-party website and transform, load these data to MariaDB as Grafana datasource.}
      \resumeSubItem{Because of the \textbf{data loss of our 3rd-party network monitoring API}  when testing with My automation teammate's API wrapper.}
      \resumeSubItem{Our crontab task keep running for \textbf{3 months} before we find another 3rd-party network monitoring service.}
      \resumeSubItem{\textbf{Tech Stack}: Python, Selenium, undetected-chromedriver, pandas, SQLAlchemy, Linux, Docker, Google Chrome,MariaDB, Grafana...etc}    
    \resumeItem{Participated in a \textbf{Long-term support project: Dragon}}
      \resumeSubItem{Which is a \textbf{video streaming platform} based on a \textbf{Open Source project: SRS and Kubernetes}.}
      \resumeSubItem{Trying to \textbf{restream live content across multiple platforms} on \textbf{server-side}.}
      \resumeSubItem{Within this project, I've focus on building \textbf{Hybrid cloud infrastructure with GCP/Alibaba Cloud}.}
      \resumeSubItem{Suvery CI/CD pipelines built with Gitlab webhook with \textbf{Tekton Pipelines} to \textbf{replace Gitlab Runner.}}
      \resumeSubItem{\textbf{Tech Stack}: Golang, Bash, Yaml, Prometheus, Grafana, ELK stack, GCP, Alibaba Cloud, CDNetworks, Linux, Docker, Kubernetes(GKE, ACK)...etc}
  \resumeItemListEnd

  \resumeSubheading
  {IoT Bootcamp}{Jan. 2021 -- May. 2021}
  {Industrial Technology Research Institute, (ITRI)}{}  
  \resumeItemListStart
    \resumeItem{Participated in a \textbf{project: IndoorAirBox}}
      \resumeSubItem{Which is a \textbf{monitoring platform} based on \textbf{Raspberry Pi, ESP8266, and related dev-tools}.}
      \resumeSubItem{\textbf{Tech Stack}: IoT , Linux, Embedded system development, Apache, C, PHP, JavaScript, CSS, HTML, Bootstrap}
  \resumeItemListEnd

  \resumeSubHeadingListEnd  

%-----------PROJECTS-----------

\section{PROJECTS}

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{homelab}} {Jun. 2023 -- Present}
        \resumeItemListStart
          \resumeItem{From \textbf{CNCF's Definition} , trying to build \textbf{lightweight Hybrid Cloud infrastructure} for \textbf{enhancement of personal tech stacks, building personal apps...etc}}
          \resumeItem{\textbf{Tech Stack}: Python, Bash, Golang, Rust, JavaScript/TypeScript, HTML5, CSS, Cloudflare, AWS, Linux ,Proxmox Virtual Environment, Docker, k3s/k0s cluster(Lightweight Kubernetes), *-exporters, Prometheus, Grafana, ELK stack, Terrform, Ansible, Github Actions, Jenkins Container Registry, service mesh (linkerd), MongoDB, PostgreSQL, MySQL, InfluxDB, ... etc}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{resume}} {Mar. 2023 -- Present}
        \resumeItemListStart
          \resumeItem{Building \textbf{a online CV website} based on \textbf{LaTeX} to record my experience, projects, education, skills.}
          \resumeItem{Render a CV file via \textbf{single HTML-CSS-JavaScript transform from PDF Source with pdf2htmlEX} or access \textbf{PDF file directly via built-in PDF viewer of browsers(Google Chrome, Brave, Firefox, Safari...etc)}}
          \resumeItem{Learning concepts of \textbf{SSR (Server-Side Rendering),  CSR (Client-Side Rendering).}}
          \resumeItem{Development and Deployment CI/CD pipelines with \textbf{Bash, Docker, GitHub} to make \textbf{Proof of concept.}}
          \resumeItem{\textbf{Tech Stack}: LaTeX, pdf2htmlEX, Bash, JavaScript/TypeScript, React, Next.js, GNU Make, Github, Linux, Docker, Nginx, Cloudflare Tunnel}
        \resumeItemListEnd          
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{setup dev environment}} {Dec. 2022 -- Present}
        \resumeItemListStart
          \resumeItem{Building \textbf{a personal notes website} based on \textbf{Material for MkDocs} to render Markdown files to web pages.}
          \resumeItem{\textbf{Tech Stack}: Python, Bash, Yaml, Markdown, Github, GitHub Actions, Linux, Docker, Nginx, Cloudflare}
        \resumeItemListEnd          
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section {EDUCATION}
\resumeSubHeadingListStart
\resumeSubheading
  {National Dong Hwa University}{Sep. 2016 -- Jan. 2019}
  {Master of Science in Materials Science and Engineering}{Shoufeng, Hualien}
    \resumeItemListStart
  \resumeItem {\textbf{Thesis}: Ultrafast Pump-probe Transient Absorption Spectroscopy of Layer-controllable Molybdenum Disulfide Films}
    \resumeItem 
        {\textbf{Research}: Semiconductor Materials }
    \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
  {National Dong Hwa University}{Sep. 2012 -- Jun. 2016}
  {Bachelor of Science in Materials Science and Engineering}{Shoufeng, Hualien}
    \resumeItemListStart
    \resumeItem {Program of Advanced Materials}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages}{: Mandarin (native), English (professional working proficiency)}\vspace{2pt} \\
     \textbf{Programming}{: Python(proficient), Bash(competence), JavaScript/HTML/CSS(competence), SQL(competence)}\vspace{2pt} \\
     \textbf{Frameworks}{: Selenium, pandas, SQLAlchemy} \\
     \textbf{Infra}{: AWS, Kubernetes, GitLab Runner, Pulumi, Ansible}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}